\documentclass{article}
\usepackage[english]{babel}
\usepackage[english]{isodate}
\usepackage[style=ieee,backend=bibtex,defernumbers=true]{biblatex}
\addbibresource{9_references-scholar.bib}
\addbibresource{9_references-other.bib}

\usepackage{amsmath}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{standalone}
\usepackage{xcolor}
\usepackage{standalone}
\usepackage{tabularx}
\usepackage{subfig}
\usepackage{csquotes}
\usepackage{float}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{subfig}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[defaultlines=5,all]{nowidow}
\usepackage{fancyhdr}
\usepackage{changepage}

\pagestyle{fancy}
\fancyhf{}
\rhead{Detecting Road Surface Anomalies using Multimodal Machine Learning}
\lhead{Joël Luijmes, 2021}
\cfoot{\thepage}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\small\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    escapeinside={``}
}

\lstset{style=mystyle}


\definecolor{light-gray}{gray}{0.95}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true,citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}

% \widowpenalties 1 10000
% \raggedbottom

\usepackage{charter}
\usepackage[parfill]{parskip}

\usepackage{enumitem}
\setlist[itemize,enumerate]{noitemsep, topsep=0.5pt}

% \bibliographystyle{IEEEtranN}

\newcommand{\authorref}[1]{\citeauthor*{#1} (\citeyear{#1}) \cite{#1}}
\newcommand{\code}[1]{%
\setlength\fboxsep{1pt}%
\colorbox{backcolour}{\lstinline{#1}}%
}


\setcounter{tocdepth}{2}

\begin{document}

\pagenumbering{arabic}

\title{
    \textbf{Detecting Road Surface Anomalies using\\
    Multimodal Machine Learning}
}
\author{
\textbf{Joël Luijmes} \\ 
\small{Student number: 2031107} \\
\small{Email: \href{mailto:me@joell.app}{me@joell.app}}
}

\date{}
\maketitle
\thispagestyle{empty}

\vskip 3cm

{\centering

THESIS SUBMITTED IN PARTIAL FULFILLMENT \\
OF THE REQUIREMENTS FOR THE DEGREE OF \\
MASTER OF SCIENCE IN DATA SCIENCE AND ENTREPRENEURSHIP \\
JHERONIMUS ACADEMY OF DATA SCIENCE

\vskip 6cm

Supervisors: \\
Prof. Dr. Willem-Jan van den Heuvel \\
Dr. Dario Di Nucci

\vskip 3cm

Jheronimus Academy of Data Science \\
1 December 2021

\par}

\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\thispagestyle{empty}

\section*{Abstract}

\begin{adjustwidth}{1cm}{2cm}
\textit{The current process of performing road maintenance takes long, is costly and largely relies on subjective observations. In recent years, the need for data driven inspection emerged to perform automatic road quality assessment. In this work, we contribute a novel method combining both visual and accelerometer data to detect road surface anomalies. We evaluate the performance of the multimodal model with that of respective unimodal models. The visual based model performs best with an precision of 0.86, followed by the hybrid fusion model with precision of 0.66. Our results indicate that multimodal machine learning is successful in detecting manholes.
}
\end{adjustwidth}


\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\thispagestyle{empty}

\tableofcontents

\input{src/1_introduction}
\input{src/2_related_work}
\input{src/3_background}
% % \input{3_methodology}
\input{src/4_data-processing}
\input{src/5_experimental-research-designs}
\input{src/6_results}
\input{src/7_discussion}
\input{src/8_conclusion}
\input{src/9_references}


\end{document}